Are we living in a depressive society?

### 2024-04-14 outputs/paper/paper.qmd
Update paper.qmd
race group 1.

The line graph in @fig-raceandtrend-graph shows the depressive disorder rates for several race and ethnicity subgroups, including Hispanic, Caucasian, African American, Asian, and Other (Non-Hispanic, other races and multiple races). Each line represents the trend within a specific subgroup, providing a visual representation of how symptom rates have evolved over the specified period.

1. **Hispanic and African American Subgroups:** These lines indicate relatively higher rates of depressive symptoms compared to other groups.

@@

This analysis highlights the variations in depressive disorder rates across different educational subgroups in the US, utilizing data from mid 2020 up to early 2024. The visualization provided in the @fig-educationandtrend-graph reveals distinct temporal trends across various education demographics, illustrating how depressive symptoms fluctuate over time among these groups.

>>>>

The analysis of depressive disorder rates among various racial and ethnic groups @fig-raceandtrend-graph reveals distinct patterns of mental health disparities from 2020 to 2024. The data, visualized through a line graph, indicates varying symptom rates across five subgroups: Hispanic, Caucasian, African American, Asian, and Other.

1. **Hispanic and African American Subgroups:** Both subgroups exhibit relatively higer rates od depressive symptoms throughout the observed period compared to other groups. This may suggest a greater impact of socio-economic and possibly systemic factors affecting these communities disproportionately. The maximum rates observed for Hispanis and African Americans were 41.10% and 41.43%, respectively, with Hispanics showing a minimum rate significantly lower at 18.77%, suggesting more substantial fluctuatinos.

@@

This analysis highlights the variations in depressive disorder rates across different educational subgroups in the US, utilizing data from mid 2020 up to early 2024. The visualization provided in the @fig-educandtrend-graph reveals distinct temporal trends across various education demographics, illustrating how depressive symptoms fluctuate over time among these groups.
